---
title: "Abac data"
author: "Linh Nguyen"
date: "December 5 2018"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
Female <- filter(abac,sex=="F")
Male <- filter(abac,sex=="M")
Druggies <- filter(abac,Ivdrug=="user")
Sexualorientation <- filter(abac,LBGT=="yes")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. I will research and analazye the effectiveness of abacavirinolol. There are 4927 different people in Abracavirinol Study.  
  
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

In this report, I will use the barplots for graphical results, column percent for numerical descriptive results, Chi-squared Test and Fisher's Test for inferential results for each different groups.  
  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
#abac data  

```{r}
results <- xtabs(~infected+treatment, data=abac)
barchartGC(results,type = "percent")
```  

The graph shows that peope who took the drug (40%) are less likely to get aids than the people who do not. However, people who took the placebo (almost 60%) is more likely to get aids than the people who do not. It seems that the drug is probably working when less people getting aids.  
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

#abac data  
```{r}
colPerc(results)
rowPerc(results)
``` 

Of all the people who got aids and taking drug, 4.04 percent of peole got infected. Of all the people who got aids and taking placebo, 5.54 percent of people got infected.  
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

#abac data  
```{r}
chisqtestGC(results, graph = TRUE)
```  
  
The p-value for all people data in Chi-squared Test is 0.0168. We reject the null hypothesis because the p-value is too low.  
  
```{r}
fisher.test(results)
```  
  
The p-value for all people data in Fisher's Test is 0.0168. This a low p-value so we reject the null hypothesis.  


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

From all the data and all the results that we gathered, we rejected the null hypothesis. We can see that the people taking abac drug are more infected than the people taking placebo.  
  