---
title: "Female data"
author: "Linh Nguyen"
data: "December 5 2018"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
Female <- filter(abac,sex=="F")
Male <- filter(abac,sex=="M")
Druggies <- filter(abac,Ivdrug=="user")
Sexualorientation <- filter(abac,LBGT=="yes")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. I will research and analazye the effectiveness of abacavirinolol. We will research on the Female data in this report. There are 2638 female in this data. 

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
In this report, I will use the barplots for graphical results, column percent for numerical descriptive results, Chi-squared Test and Fisher's Test for inferential results for Female group.  
  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
#Female data 

```{r}
results2 <- xtabs(~infected+treatment, data=Female)
barchartGC(results2,type = "percent")
```  

The graph shows that females who got aids have higher percentages of taking drug that females who did not have aids. However, those who got aids have lower percentage of taking placebo than who did not get aids.  
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

#Female data  
```{r}
colPerc(results2)
rowPerc(results2)
```
Of all the female who took drug, 3.96 percent of them became infected. When they took placebo, only 2.59 percent became infected.  
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
#Female data  
```{r}
chisqtestGC(results2, graph = TRUE)
```
  
The Chi-squared Test shows that the female data has the p-value of 0.062, so we failed to reject the hypothesis.  

```{r}
fisher.test(results2)
```
  
The Fisher's test shows that the female data has the p-value of 0.04911, so we reject the hypothesis. However, because we failed to treject the hypotheiss in the Chi-squared Test, the results are inconclusive.
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
From the data, we can conclude that the drug does not actually work on the females. We failed to to reject the hypothesis based on the Chi-squared Test and the Fisher's Test.  






